Brownian Dynein Model

### 2015-07-28 latex/derivation.tex
Prepare equations for matrix form.

>>>>

\section{Preparing Equations for Matrix Form}

\begin{multline}
\dot{\Theta}_{br} =
\big(\sin(\Theta_{br}-\pi)\sin(\Theta_{bl}) - \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big)\dot{\Theta}_{bl} + 
\frac{L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) - L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_{t}}\dot{\Theta}_{ml}  + \\
\frac{L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{t}}\dot{\Theta}_{mr} - 
\frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{t}} - 
\frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{t}}
\end{multline}

\begin{multline}
\dot{\Theta}_{mr} =
\frac{2L_{t}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{t}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{s}}\dot{\Theta}_{bl} + 
\big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{mr}-\pi) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{ml} + \\
\big( \mn \cos(\Theta_{mr}-\pi)\cos(\Theta_{mr}-\pi) + \mn\sin(\Theta_{mr}-\pi)\sin(\Theta_{mr}-\pi)\big)\dot{\Theta}_{mr} + 
\frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{s}}\dot{\Theta}_{br} + \\
\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{s}\gamma} + \\
\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{s}}
\end{multline}

\begin{multline}
\dot{\Theta}_{ml} =
\frac{\mn 3L_{t}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{t}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{bl} + 
\big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{ml})\cos(\Theta_{ml}) \big)\dot{\Theta}_{ml} + \\
\big(\mn 2\sin(\Theta_{mr}-\pi)\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{mr} + 
\frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{br} + \\
\frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
\frac{\sin(\Theta_{ml})R_{xt } + \mn \cos(\Theta_{ml})R_{yt } + \sin(\Theta_{ml})R_{xmr} + \mn \cos(\Theta_{ml})R_{ymr} + \sin(\Theta_{ml})R_{xbr} + \mn \cos(\Theta_{ml})R_{ybr}}{L_s}
\end{multline}

\begin{multline}
\dot{\Theta}_{bl} =
\big(\mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) \big)\dot{\Theta}_{bl} +
\frac{\mn 3L_{s}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{s}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{ml} + \\
\frac{\mn 2L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} +
\big(\mn \sin(\Theta_{bl}) \sin(\Theta_{br}-\pi) + \mn \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big) \dot{\Theta}_{br} + \\
\frac{\sin(\Theta_{bl})F_{xml} + \mn\cos(\Theta_{bl})F_{yml} + \sin(\Theta_{bl})F_{xt } + \mn \cos(\Theta_{bl})F_{yt } + \sin(\Theta_{bl})F_{xmr} + \mn \cos(\Theta_{bl})F_{ymr} + \sin(\Theta_{bl})F_{xbr} + \mn \cos(\Theta_{bl})F_{ybr}}{\gamma L_t} + \\
\frac{\sin(\Theta_{bl})R_{xml} + \mn \cos(\Theta_{bl})R_{yml} + \sin(\Theta_{bl})R_{xt } + \mn \cos(\Theta_{bl})R_{yt} + \sin(\Theta_{bl})R_{xmr} + \mn \cos(\Theta_{bl})R_{ymr} + \sin(\Theta_{bl})R_{xbr} + \mn \cos(\Theta_{bl})R_{ybr}}{L_t}
\end{multline}

\section{All velocity terms on LHS:}

\begin{multline}
\big(\sin(\Theta_{br}-\pi)\sin(\Theta_{bl}) - \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big)\dot{\Theta}_{bl} + 
\frac{L_{s}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) - L_{s}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_{t}}\dot{\Theta}_{ml}  + \\
\frac{L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{br}-\pi) - L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{br}-\pi)}{L_{t}}\dot{\Theta}_{mr} +
\mn\dot{\Theta}_{br} =
\frac{\sin(\Theta_{br}-\pi)F_{xbr} + \cos(\Theta_{br}-\pi)F_{ybr}}{\gamma L_{t}} + \\
\frac{\sin(\Theta_{br}-\pi)R_{xbr} + \cos(\Theta_{br}-\pi)R_{ybr}}{L_{t}}
\end{multline}

\begin{multline}
\frac{2L_{t}\cos(\Theta_{bl})\cos(\Theta_{mr}-\pi) + \mn 2L_{t}\sin(\Theta_{bl})\sin(\Theta_{mr}-\pi)}{L_{s}}\dot{\Theta}_{bl} + 
\big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{mr}-\pi) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{ml} + \\
\big( \mn \cos(\Theta_{mr}-\pi)\cos(\Theta_{mr}-\pi) + \mn\sin(\Theta_{mr}-\pi)\sin(\Theta_{mr}-\pi) - 1\big)\dot{\Theta}_{mr} + 
\frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{mr}-\pi) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{mr}-\pi)}{L_{s}}\dot{\Theta}_{br} = \\
\mn\frac{\sin(\Theta_{mr}-\pi)F_{xmr} + \sin(\Theta_{mr}-\pi)F_{xbr} - \cos(\Theta_{mr}-\pi)F_{ymr} - \cos(\Theta_{mr}-\pi)F_{ybr}}{L_{s}\gamma} + \\
\mn\frac{\sin(\Theta_{mr}-\pi)R_{xmr} + \sin(\Theta_{mr}-\pi)R_{xbr} - \cos(\Theta_{mr}-\pi)R_{ymr} - \cos(\Theta_{mr}-\pi)R_{ybr}}{L_{s}}
\end{multline}

\begin{multline}
\frac{\mn 3L_{t}\sin(\Theta_{bl})\sin(\Theta_{ml}) + \mn3L_{t}\cos(\Theta_{bl})\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{bl} + 
\big(\mn 2\sin(\Theta_{ml})\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{ml})\cos(\Theta_{ml}) - 1\big)\dot{\Theta}_{ml} + \\
\big(\mn 2\sin(\Theta_{mr}-\pi)\sin(\Theta_{ml}) + \mn 2\cos(\Theta_{mr}-\pi)\cos(\Theta_{ml}) \big)\dot{\Theta}_{mr} + 
\frac{\mn L_{t}\sin(\Theta_{br}-\pi)\sin(\Theta_{ml}) + \mn L_{t}\cos(\Theta_{br}-\pi)\cos(\Theta_{ml})}{L_s}\dot{\Theta}_{br} = \\
\mn \frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
\mn \frac{\sin(\Theta_{ml})R_{xt } + \mn \cos(\Theta_{ml})R_{yt } + \sin(\Theta_{ml})R_{xmr} + \mn \cos(\Theta_{ml})R_{ymr} + \sin(\Theta_{ml})R_{xbr} + \mn \cos(\Theta_{ml})R_{ybr}}{L_s}
\end{multline}

\begin{multline}
\big(\mn 3\sin(\Theta_{bl})\sin(\Theta_{bl})\mn + 3\cos(\Theta_{bl})\cos(\Theta_{bl}) -1\big)\dot{\Theta}_{bl} +
\frac{\mn 3L_{s}\sin(\Theta_{ml})\sin(\Theta_{bl}) + \mn 3L_{s}\cos(\Theta_{ml})\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{ml} + \\
\frac{\mn 2L_{s}\sin(\Theta_{mr}-\pi)\sin(\Theta_{bl}) + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\cos(\Theta_{bl})}{L_t}\dot{\Theta}_{mr} +
\big(\mn \sin(\Theta_{bl}) \sin(\Theta_{br}-\pi) + \mn \cos(\Theta_{br}-\pi)\cos(\Theta_{bl})\big) \dot{\Theta}_{br} = \\
\mn \frac{\sin(\Theta_{bl})F_{xml} + \mn\cos(\Theta_{bl})F_{yml} + \sin(\Theta_{bl})F_{xt } + \mn \cos(\Theta_{bl})F_{yt } + \sin(\Theta_{bl})F_{xmr} + \mn \cos(\Theta_{bl})F_{ymr} + \sin(\Theta_{bl})F_{xbr} + \mn \cos(\Theta_{bl})F_{ybr}}{\gamma L_t} + \\
\mn \frac{\sin(\Theta_{bl})R_{xml} + \mn \cos(\Theta_{bl})R_{yml} + \sin(\Theta_{bl})R_{xt } + \mn \cos(\Theta_{bl})R_{yt} + \sin(\Theta_{bl})R_{xmr} + \mn \cos(\Theta_{bl})R_{ymr} + \sin(\Theta_{bl})R_{xbr} + \mn \cos(\Theta_{bl})R_{ybr}}{L_t}
\end{multline}
